Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-29 paper/paper.tex
Tiny fixes
Make the references more consistent

\bibitem{syntaxforfree}
R. Atkey.  Syntax for Free: Representing Syntax with Binding Using
Parametricity.  Proceedings, Typed Lambda Calculi and Applications,
pp. 35-49, 2009.

@@

\bibitem{benton06reading}
N.~Benton, A.~Kennedy, M.~Hofmann, L.~Beringer.
Reading, Writing and Relations.
Proceedings, Asian Symposium on Programming Languages and Systems,
pp. 114-130, 2006.

@@

\bibitem{Cardelli}
L.~Cardelli, P.~Gardner.
Processes in Space.
{\em Programs, Proofs, Processes}: Proc, 6th Conference on Computability in Europe, pp 78-87, LNCS vol. 6158, 2010.

@@

\bibitem{harrison09without}
J.~Harrison.
Without Loss of Generality.
Proceedings, Theorem Proving in Higher Order Logics,
pp. 43-59, 2009.

@@

\bibitem{jones95functional}
M.~P.~Jones.  Functional Programming with Overloading and Higher-Order
Polymorphism. Proceedings, Advanced Functional Programming,
pp. 97-136, 1995.

@@

\bibitem{wadler89theorems}
P.~Wadler.  Theorems for Free!.  Proceedings, International Conference
on Functional Programming Languages and Computer Architecture,
pp. 347-359, 1989.

>>>>

\bibitem{syntaxforfree}
R. Atkey.  Syntax for Free: Representing Syntax with Binding Using
Parametricity.  Proceedings, TLCA,
pp. 35-49, 2009.

@@

\bibitem{benton06reading}
N.~Benton, A.~Kennedy, M.~Hofmann, L.~Beringer.
Reading, Writing and Relations.
Proceedings, APLAS,
pp. 114-130, 2006.

@@

\bibitem{Cardelli}
L.~Cardelli, P.~Gardner.
Processes in Space.
{\em Programs, Proofs, Processes}: Proceedings, CiE, pp. 78-87, 
%LNCS vol. 6158, 
2010.

@@

\bibitem{harrison09without}
J.~Harrison.
Without Loss of Generality.
Proceedings, TPHOLs,
pp. 43-59, 2009.

@@

\bibitem{jones95functional}
M.~P.~Jones.  Functional Programming with Overloading and Higher-Order
Polymorphism. Proceedings, AFP,
pp. 97-136, 1995.

@@

\bibitem{wadler89theorems}
P.~Wadler.  Theorems for Free!.  Proceedings, FPCA,
pp. 347-359, 1989.
